Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture \todo{? more application oriented''}

### 2013-10-19 ieee_paper.tex
minor

\author{\IEEEauthorblockN{Gordon Erlebacher\IEEEauthorrefmark{1},
Erik Saule\IEEEauthorrefmark{2}, Natasha Flyer\IEEEauthorrefmark{3}, 
and Evan Bollig\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Scientific Computing, 
Florida State University\\ %, Tallahassee %FL 32306-4120\\
Email: gerlebacher@fsu.edu, bollig@gmail.com}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Department of Computer Science, University of North Carolina at Charlotte\\
Email: erik.saule@uncc.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Computational and Information Systems Laboratory, UCAR \\
Email: flyer@ucar.edu}}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Department of Scientific Computing, Florida State University\\
%Email: bollig@gmail.com}\todo{check affiliation fsu's are strange.}}
\maketitle

@@

In this work, we use an Intel Xeon Phi 5110P coprocessor. This card
has 8 memory controllers that can each execute 5 billion
transactions per second. Each has two 32-bit channels, achieving a total
bandwidth of 320~GB/s aggregated across all the memory
controllers. There are 60 cores clocked at 1.05~GHz. Their memory
interfaces are 32-bit wide with two channels and the total bandwidth
is 8.4~GB/s per core. Thus, the cores should be able to consume 504~GB/s
at most. However, the bandwidth between the cores and the memory
controllers is limited by the ring network that connect the cores and
the memory controller. Its precise bandwidth is unknown but it is
believed to be between 200~GB/s and 250~GB/s.

>>>>

\author{\IEEEauthorblockN{Gordon Erlebacher\IEEEauthorrefmark{1},
Erik Saule\IEEEauthorrefmark{2}, Natasha Flyer\IEEEauthorrefmark{3}, 
and Evan Bollig\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Scientific Computing, 
Florida State University\\ %, Tallahassee %FL 32306-4120\\
}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Department of Computer Science, University of North Carolina at Charlotte\\
}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Computational and Information Systems Laboratory, UCAR \\
}
Email: gerlebacher@fsu.edu, esaule@uncc.edu, flyer@ucar.edu, bollig@gmail.com }
\maketitle

@@

In this work, we use an Intel Xeon Phi 5110P coprocessor. This card
has 8 memory controllers that can each execute 5 billion
transactions per second. Each has two 32-bit channels, achieving a total
bandwidth of 320~GB/s aggregated across all the memory
controllers. There are 60 cores clocked at 1.05~GHz. Their memory
interfaces are 32-bit wide with two channels and the total bandwidth
is 8.4~GB/s per core. Thus, the cores should be able to consume 504~GB/s
at most. However, the bandwidth between the cores and the memory
controllers is limited by the ring network that connects the cores and
the memory controller. Its precise bandwidth is unknown but it is
believed to be between 200~GB/s and 250~GB/s.
